---
title: "Lab5"
author: "Sarang Patel"
date: "3/23/2022"
output: github_document
---

```{r}
library(devtools)
library(tidyverse)
library(dplyr)
library(corrplot)
```


https://github.com/sarangpmr/bball/

# Package Setup
## Question 1

The three functions have been created and added to an R package (following the processes in "Intro to R package….R").
They can be found in the public repo [HERE](https://github.com/sarangpmr/bball/tree/main/R).
There are three functions total:
* Function 1: lebronPPG.R
    + This function takes the PPG for Lebron James for a given NBA season (one of the seasons that he has played).
* Function 2: oldestPlayer.R
    + This function returns the oldest player for a given NBA season.
* Function 3: corrNum.R
    + This function returns the correlation matrix for all numeric variables in a given year.

## Question 2

The package has been created.

## Question 3

The package has been uploaded to Github (correctly, this time). It can be found [HERE](https://github.com/sarangpmr/bball/).

# Package Usage
## Question 4
Let's now install the package in R. 
```{r}
install_github("sarangpmr/bball")
library(bball)
```

## Question 5
Let's now run each of the functions and make sure they are working correctly.

Testing out that the .Rda file correctly imports a data frame:
```{r}
# test out the .Rda file works correctly and returns a data frame.
data(nba)
class(nba)
head(nba, 10)
```

Testing out that the first function, lebronPPG():
```{r}
# test out the first function, lebronPPG()
lebronPPG(2001) # this should return an error
lebronPPG(2006)
```

Testing out the second function, oldestPlayer():
```{r}
oldestPlayer(1990)
```

Testing out the third function, corrNum():
```{r}
corrNum(2006)
```


